Exploring Rural Shrink Smart Through Guided Discovery Dashboards

### 2021-12-23 SCCAbstract_SDSS2022-knitr.Rnw
A few more changes

% File SDSS2020_SampleExtendedAbstract.tex
\documentclass[10pt]{article}
\usepackage{newtxtext, newtxmath, times}
\usepackage{sdss2020} % Uses Times Roman font (either newtx or times package)
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath, amsfonts}
\usepackage{algorithm, algorithmic}  
\usepackage{graphicx}
% Commands for editing
\newcommand{\db}[1]{{\textcolor{orange}{#1}}}
\newcommand{\svp}[1]{{\textcolor{blue}{#1}}}

@@

\section{Data Description}
{\it Iowa Data} were used to create the SCC dashboard. {\it Iowa Data} is a public data website that collects and updates data on the State of Iowa Government, data are mostly on a town/city level that is not collected in National Data Collection Systems. {\it Iowa Data} website is a unique and detailed database of information about residents, such as liquor sales and school building locations. For the purpose of the Rural Shrink Smart Dashboard, we will collect as much data as possible, such as obtaining fire department and hospital details. These data are collected on all towns that are available. We will use statistical clustering methods will be used to determine the town classifications to help improve the rural towns.

\section{Data Challenges}
{\it Iowa Data} website has an exhaustive and detailed data, but that data collected has missing information. This information can be broken down into two separate types, in which we will call a true missing, a particular service that is missing because the town does not have or offer the service to the community. For example, many small towns do not have a hospital that will only cater to the community, but they will have access to a hospital in a neighboring town. The second type of missing data are when data should be available and are not currently being collected in the data but are available in a different data source. For example, our public school data does not actual represent public schools in bigger cities, suggesting that the closest Elementary school is 20 miles away, which we understood that to be untrue. This type of missing data is very typical in data collection, but could led our research in a poor direction.

\section{Guiding Design Principles}
Dashboards have a variety of challenges, our research will focus on users' challenges with understanding data and statistical relationships of dashboards. We investigate user interaction strategies that will not challenge the knowledge of the analyst in a variety of backgrounds. With little research on the adaptation of dashboards, we will particularly focus on the techniques that to solve interaction and information presentation challenges. In our research, we would like to use a guiding design principles to develop and design the following:
\begin{itemize}
\item Showing a town analyst with peers to help with changes that improved the QoL
\item Dashboard design that will make the town the main focus without distracting the analysts with peer comparisons
\item Creating a feedback loop that will, assist in the guided discovery from the analysts
\end{itemize}

>>>>

% File SDSS2020_SampleExtendedAbstract.tex
\documentclass[10pt]{article}
\usepackage{newtxtext, newtxmath, times}
\usepackage{sdss2020} % Uses Times Roman font (either newtx or times package)
\usepackage{url}
\usepackage{latexsym}
\usepackage{amsmath, amsfonts}
\usepackage{algorithm, algorithmic}  
\usepackage{graphicx}
\usepackage[dvipsnames]{xcolor} % colors

% Commands for editing
\newcommand{\db}[1]{{\textcolor{orange}{#1}}}
\newcommand{\svp}[1]{{\textcolor{blue}{#1}}}

@@

\section{Data Description}
\svp{Data collected from \url{data.iowa.gov}} were used to create the SCC dashboard. \svp{Most of these datasets are collected on a town/city or county level, requiring us to carefully join data accounting for differences in spatial resolution.} \svp{\url{data.iowa.gov} contains unique information about residents, including local liquor sales, school building locations, town budgets and expenditures, hospital beds, Medicaid reimbursements, and other details that may provide information about local quality of life.} 
\svp{Using this data, we created a dashboard which allows communities to explore these data and compare and contrast their local community to other communities of similar size and location. In addition to manual comparisons created by the user, we will use statistical clustering methods to identify groups of towns which employ similar strategies to maintain resident quality of life.}

\svp{One of the interesting features of this assembled dataset is that missing data can be missing for multiple reasons: not all state data is complete, but data about certain services may also be missing because towns do not offer that service.}
\svp{Thus, in addition to the usual challenges of working with real-world data that is "messy" in a variety of ways, we also have to contend with missing data that is missing due to the size of the community or the lack of services. This makes both visualization and statistical analysis more complicated.}

\section{Guiding Design Principles}
\svp{An additional challenge is that research on dashboard creation and interactive visualization tends to be very task-specific and not generalizable. That is, it is relatively easy to create a dashboard that works for a particular task, but it is hard to generalize from that process what will work for the next dashboard. With this in mind, we have clearly documented our intentions at each stage of the design and evaluation process, with the goal of gathering some useful information about general dashboard design from the process of creating this specific dashboard.}
\svp{Thus, our initial set of dashboard design principles is as follows: }
\begin{itemize}
\item \svp{The town leaders are the focus audience; thus, the town itself should be the central focus of the app.}
\item \svp{Facilitate comparisons with other towns in order to allow the user to explore other potential solutions to offering services that enhance resident quality of life.}
\item \svp{Present the user with peer comparisons in order to widen the scope of exploration beyond the initial set of obvious peers in the local region.}
\item \svp{Allow for more detailed data and feature requests to improve the dashboard design over time.}
\end{itemize}
